---
title: "2015 Yearly Analysis"
output: 
  rmdformats::readthedown:
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The data for the year 2015 gives us a benchmark to base our analysis on as 2015 was the first year in business for the given company.

## Preparing Data for Analysis: 

In order to prepare our data, we're going to load all the data present in excel sheets in the form of lists.
We're gonna implement the same by using the `rbind` function.

Initially, we're going to add the paths to all of our data for the year 2015 load it into a variable named `Trips`  
```{r}
library("readxl")
library("ggplot2")
library("dygraphs")
setwd("D:/Case Study")
paths2015 <- vector()
paths2015 <- c(paths2015, paste(getwd(),"/Yearly_Data/2015/Quarterly/Divvy_Trips_2015_07.xlsx", sep = ""))
paths2015 <- c(paths2015, paste(getwd(),"/Yearly_Data/2015/Quarterly/Divvy_Trips_2015_07.xlsx", sep = ""))
paths2015 <- c(paths2015, paste(getwd(),"/Yearly_Data/2015/Quarterly/Divvy_Trips_2015_07.xlsx", sep = ""))
paths2015 <- c(paths2015, paste(getwd(),"/Yearly_Data/2015/Quarterly/Divvy_Trips_2015_07.xlsx", sep = ""))
paths2015 <- c(paths2015, paste(getwd(),"/Yearly_Data/2015/Quarterly/Divvy_Trips_2015_07.xlsx", sep = ""))
paths2015 <- c(paths2015, paste(getwd(),"/Yearly_Data/2015/Quarterly/Divvy_Trips_2015_07.xlsx", sep = ""))
AllPaths <- c(paths2015)
Trips <- list()
for(i in AllPaths)
{
  for(Mypath in i)
  { 
    Trips <- rbind(Trips,read_excel(Mypath, col_types = c("guess","guess","guess","guess","guess","guess","guess","guess","guess","guess","guess","numeric")))
  }
}
```

## Summary of Data: 

```{r}
summary(Trips)
```
## Analysis Metrics: 

* Customer-Sub Ratio
* Gender Demographic
* Trip Duration

## Customer-Sub Ratio:

The Customer-Sub Ratio metric enables us to understand the common population demographic and figure out how likely a customer is to sub to the bike rental service.

The data collected here would be used as a benchmark in the upcoming years as a metric of performance.

```{r}
UserTypeCol <- Trips$usertype
Subs <- 0
Customers <- 0

for(i in UserTypeCol)
  if(i == "Subscriber")
    Subs <- Subs + 1 else
      Customers <- Customers + 1
pie(c(Subs,Customers),label = c(paste("Subscribers = ", round(Subs*100/(Subs + Customers), 2), "%"), paste("Customers = ", round(Customers*100/(Subs + Customers), 2), "%")))
```

## Gender Demographic: 

Understanding the Gender demographic is key. This allows us to both understand who our target audience is and also if we're lacking severely in advertising to a specific gender.


```{r}
ggplot(data = Trips) +
  geom_bar(mapping = aes(x = gender, fill = usertype), stat = "count")
```

## Trip Duration: 
```{r}
ggplot(data = Trips, aes(trip_id, tripduration)) +
        geom_smooth()
```
