---
title: "2018 Yearly Analysis"
output:
  rmdformats::readthedown:
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Preparing Data for Analysis:

In order to prepare our data for analysis, we are going to load all our data in the form of lists.
We are going to do the same by providing the paths to all the data and binding them together using `rbind()` function.
The data for the financial year is now stored in the the variable `Trips`.

```{r}
library("readxl")
library("ggplot2")
library("dygraphs")
setwd("D:/Case Study")
paths2018 <- vector()
paths2018 <- c(paths2018, paste(getwd(),"/Yearly_Data/2018/Quarterly/Divvy_Trips_2018_Q1.xlsx", sep = ""))
paths2018 <- c(paths2018, paste(getwd(),"/Yearly_Data/2018/Quarterly/Divvy_Trips_2018_Q2.xlsx", sep = ""))
paths2018 <- c(paths2018, paste(getwd(),"/Yearly_Data/2018/Quarterly/Divvy_Trips_2018_Q3.xlsx", sep = ""))
paths2018 <- c(paths2018, paste(getwd(),"/Yearly_Data/2018/Quarterly/Divvy_Trips_2018_Q4.xlsx", sep = ""))
AllPaths <- c(paths2018)
Trips <- list()
for(i in AllPaths)
{
  for(Mypath in i)
  {
    Trips <- rbind(Trips,read_excel(Mypath, col_types = c("guess","guess","guess","guess","guess","guess","guess","guess","guess","guess","guess","numeric")))
  }
}
```

## Summary of Data:

```{r}
summary(Trips)
```
## Analysis Metrics:

* Customer-Sub Ratio
* Gender Demographic
* Month by Month

## Customer-Sub Ratio:

The Customer-Sub ratio seems to start plateauing around the 80 - 20 % mark. 
Which looking at the industry standard is a healthy Customer-Sub ratio.
```{r}
UserTypeCol <- Trips$usertype
Subs <- 0
Customers <- 0

for(i in UserTypeCol)
  if(i == "Subscriber")
    Subs <- Subs + 1 else
      Customers <- Customers + 1
pie(c(Subs,Customers),label = c(paste("Subscribers = ", round(Subs*100/(Subs + Customers), 2), "%"), paste("Customers = ", round(Customers*100/(Subs + Customers), 2), "%")))
```

## Gender Demographic

The Gender Demographic seems to be a recurring problem every year. It would really be in the bike rental service's best interest to advertise extensively to increase the sex ratio and further increase profits.
```{r}
ggplot(data = Trips) +
  geom_bar(mapping = aes(x = gender, fill = usertype), stat = "count")
```

## Month by Month:

Before Looking at each month of the year, we need to change our date formats to enable us to use those metrics.
Using the `as.Date()` method, we create a new column named `month` recording the month the trip started in.
```{r}
Trips$month <- format(as.Date(Trips$start_time), "%m")
```

We can observe, the same pattern appears in this year's analysis as well.
People tend to make more trips using the bike rental service during the summer season which is consistent with the findings shown in the previous years discussing the possibility of advertising for summer season in order to drive profits.
```{r}
xy2 <- as.data.frame(table(Trips$month))
xy2$Var1 <- factor(xy2$Var1, levels = xy2$Var1[order(xy2$Freq)])

ggplot(xy2,aes(x=Var1, y = Freq, fill = Freq)) +
    scale_fill_gradient(low = "yellow", high = "red") +
      geom_bar(width=0.7, stat = "identity") +
        coord_flip()
```
